Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-11 paper/paper.tex
Committing from 38,000ft

For both subgraph isomorphism and maximum common subgraph, constraint programming is the best known
approach\footnote{Note that toolkits are not used, to facilitate better memory layouts and
propagation queues, although the algorithms are heavily inspired by the constraint programming
literature}. For both problems, we create a variable for each vertex in the pattern graph (the
smaller graph, in the case of maximum common subgraph), with domains ranging over the vertices in
the target graph (the larger graph). For maximum common subgraph, each domain is given an additional
$\bot$ value, meaning ``unmapped''.

We also have constraints for adjacency and non-adjacency. For the maximum common subgraph case,
$\bot$ is ignored.

In our algorithm we make use of \cref{prop:comp} by seeking an $i$ which simultaneously satisfies $P
\rightarrowtail T$ and $\loopcomp{P} \rightarrowtail \loopcomp{T}$ when searching for an induced subgraph
isomorphism.  Further, \cref{prop:comp} tells us that every induced subgraph isomorphism is
equivalent to simultaneous non-induced subgraph isomorphisms both $P$ and $T$ as well as their
complements.

@@

A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
between $P$ and $T$ with $k$ extra universally-adjacent vertices added to $T$. However, using such
an approach is not ideal, because it would introduce symmetries; for induced $k$-less-subgraph
isomorphisms, an approach based around adding vertices to $T$ cannot work at all.

Another algorithmic approach could be to try each way of removing $k$ vertices from the pattern
graph, and solving the subgraph isomorphism problem in turn. This approach might be feasible for $k
= 1$, although it would involve a lot of duplication of search effort, but for larger values of $k$
the number of searches which would have to be made would grow very quickly.

Finally, for the induced case we could try adapting maximum common subgraph algorithms to solve the
decision problem. However, both the maximum common subgraph algorithm and the clique encoding
require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$ memory, which is extremely problematic on the
instances we wish to work with.

@@

\section{Experimental Setup}

@@

\subsection{Solving from the Top Down}

\section{Conclusion}

>>>>

For both subgraph isomorphism and maximum common subgraph, constraint programming is the best known
approach\footnote{Note that toolkits are not used in state of the art implementations, to facilitate
better memory layouts and propagation queues, although the algorithms are heavily inspired by
constraint programming.}. For both problems, we create a variable for each vertex in the
pattern graph (the smaller graph, in the case of maximum common subgraph), with domains ranging over
the vertices in the target graph (the larger graph). For maximum common subgraph, each domain is
given an additional $\bot$ value, meaning ``unmapped''.

Constraints are used to ensure that adjacency pairs of vertices are mapped to adjacenct pairs of
vertices. For the maximum common subgraph case, any pair of assignments with $\bot$ as either value
is also permitted.  To handle the induced case, rather than the more usual approach of directly
having constraints for non-adjacent pairs of vertices, we will make use of \cref{prop:comp} by
seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
\rightarrowtail \loopcomp{T}$.

@@

A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
between $P$ and $T$, with $k$ extra universally-adjacent vertices added to $T$. However, using such
an approach is not ideal, because it would introduce symmetries; for induced $k$-less-subgraph
isomorphisms, an approach based around adding vertices to $T$ cannot work at all.
Another algorithmic approach could be to try each way of removing $k$ vertices from the pattern
graph, and solving the subgraph isomorphism problem in turn. This approach might be feasible for $k
= 1$, although it would involve a lot of duplication of search effort, but for larger values of $k$
the number of searches which would have to be made would grow very quickly.
Finally, for the induced case we could try adapting maximum common subgraph algorithms to solve the
decision problem. However, both the maximum common subgraph algorithm and the clique encoding
require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$ memory, which is extremely problematic on the
instances we wish to work with.

@@

\subsection{Experimental Setup}

@@

\subsection{Solving from the Top Down}
\section{Conclusion}
